Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package

### 2020-10-12 paper.tex

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package},
            pdfauthor={Joshua Rosenberg, Caspar van Lissa, Jennifer Schmidt, Patrick Beymer, Daniel Anderson, \& Matthew Schell},
            pdfkeywords={Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{tidyLPA}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Tennessee, Knoxville\\\textsuperscript{2} Utrecht University\\\textsuperscript{3} Michigan State University\\\textsuperscript{4} University of Oregon\\\textsuperscript{5} }
\keywords{Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust\newline\indent Word count: }
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother

\title{Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package}
\author{Joshua Rosenberg\textsuperscript{1}, Caspar van Lissa\textsuperscript{2}, Jennifer Schmidt\textsuperscript{3}, Patrick Beymer\textsuperscript{3}, Daniel Anderson\textsuperscript{4}, \& Matthew Schell\textsuperscript{3}}
\date{}

\authornote{

Correspondence concerning this article should be addressed to Joshua Rosenberg, 1122 Volunteer Blvd., Knoxville, TN, 37996. E-mail: \href{mailto:jmrosenberg@utk.edu}{\nolinkurl{jmrosenberg@utk.edu}}}

\abstract{

}

@@

\begin{verbatim}
## Warning: package 'tibble' was built under R version 3.6.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'purrr' was built under R version 3.6.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'dplyr' was built under R version 3.6.2
\end{verbatim}

@@

We wish to note that challenge facing the analyst using LPA is that these
parameters and the distinct model parameterizations that can be estimated is the
different terminology used. As one example, Scrucca et al. (2017) refer to these
parameterizations not in terms of whether and how parameters are estimated, but
rather in terms of the geometric properties of the distributions that result
from particular parameterizations. Muthen and Muthen (1997-2017) and others
(Pastor et al., 2007) commonly refer to local independence to mean that the
covariances are fixed to zero (also described as the specification of the
covariance matrix as \enquote{diagonal,} because only the diagonal components, or the
variances, are estimated).

@@

\begin{verbatim}
## Warning: package 'tidyLPA' was built under R version 3.6.2
\end{verbatim}

@@

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_4_class_1, model_4_class_2, model_4_class_3, model_4_class_4, model_4_class_5, model_4_class_6, model_4_class_7, model_4_class_8, model_4_class_9, model_5_class_1, model_5_class_2, model_5_class_3, model_5_class_4, model_5_class_5, model_5_class_6, model_5_class_7, model_5_class_8, model_5_class_9, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_4_class_1, model_4_class_2, model_4_class_3, model_4_class_4, model_4_class_5, model_4_class_6, model_4_class_7, model_4_class_8, model_4_class_9, model_5_class_1, model_5_class_2, model_5_class_3, model_5_class_4, model_5_class_5, model_5_class_6, model_5_class_7, model_5_class_8, model_5_class_9, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

@@

\hypertarget{htmlwidget-31a3e9100620ea87273d}{}

@@

This section highlights three general recommendations. First, scholars taking a
person-oriented approach should emphasize reproducibility in carrying out
analyses. This is in part due to the exploratory and interpretative nature of
person-oriented approaches. To this end, presenting multiple models, as in
Pastor et al. (2007), should be encouraged, rather than presenting one solution.
In addition, having multiple analysts review the solutions found is encouraged.
As part of this recommendation, we suggest that researchers consider how their
analyses can be reproduced by other analysts outside of the research team:
Sharing code and data is an important part of this work. Also related,
researchers should consider how profiles are replicated across samples.

@@

First, we note that developing a tool that emphasized both rigor and access has
been, so far, well-received. This suggests that there is an audience (or a
market) for tools to carry out sophisticated tools that may be otherwise
out-of-reach. Tools do not need to be hard to use, a point made by developers
of, for example, tools to carry out highly-sophisticated Bayesian methods using
the most cutting-edge tools (Bürkner \& others, 2017, Makowski, Ben-Shachar, Chen, and Lüdecke (2019)). We think
that tidyLPA speaks to this, too.

@@

\leavevmode\hypertarget{ref-R-tidyLPA}{}%
Rosenberg, J. M., Beymer, P. N., Anderson, D. J., Lissa, C. van, \& Schmidt, J. A. (2018). TidyLPA: An r package to easily carry out latent profile analysis (lpa) using open-source or commercial software. \emph{Journal of Open Source Software}, \emph{3}(30), 978. doi:\href{https://doi.org/10.21105/joss.00978}{10.21105/joss.00978}

\leavevmode\hypertarget{ref-burkner2017}{}%
Bürkner, P.-C., \& others. (2017). Brms: An r package for bayesian multilevel models using stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.

\leavevmode\hypertarget{ref-R-tidyLPA}{}%
Rosenberg, J. M., Beymer, P. N., Anderson, D. J., Lissa, C. van, \& Schmidt, J. A. (2018). TidyLPA: An r package to easily carry out latent profile analysis (lpa) using open-source or commercial software. \emph{Journal of Open Source Software}, \emph{3}(30), 978. doi:\href{https://doi.org/10.21105/joss.00978}{10.21105/joss.00978}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package},
  pdflang={en-EN},
  pdfkeywords={Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{tidyLPA}
\author{Joshua Rosenberg\textsuperscript{1}, Caspar van Lissa\textsuperscript{2}, Jennifer Schmidt\textsuperscript{3}, Patrick Beymer\textsuperscript{3}, Daniel Anderson\textsuperscript{4}, \& Matthew Schell\textsuperscript{3}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Tennessee, Knoxville\\\textsuperscript{2} Utrecht University\\\textsuperscript{3} Michigan State University\\\textsuperscript{4} University of Oregon\\\textsuperscript{5} }
\authornote{

Correspondence concerning this article should be addressed to Joshua Rosenberg, 1122 Volunteer Blvd., Knoxville, TN, 37996. E-mail: jmrosenberg@utk.edu}
\keywords{Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust\newline\indent Word count: }
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package}

\date{}

@@

@@

We wish to note that challenge facing the analyst using LPA is that these
parameters and the distinct model parameterizations that can be estimated is the
different terminology used. As one example, Scrucca et al.~(2017) refer to these
parameterizations not in terms of whether and how parameters are estimated, but
rather in terms of the geometric properties of the distributions that result
from particular parameterizations. Muthen and Muthen (1997-2017) and others
(Pastor et al., 2007) commonly refer to local independence to mean that the
covariances are fixed to zero (also described as the specification of the
covariance matrix as \enquote{diagonal,} because only the diagonal components, or the
variances, are estimated).

@@

@@

\begin{verbatim}
## tidyLPA analysis using mclust: 
## 
##  Model Classes AIC      BIC      Entropy prob_min prob_max n_min n_max BLRT_p
##  1     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  1     2       79307.22 79422.47 0.59    0.86     0.89     0.44  0.56  0.01  
##  1     3       79297.86 79455.02 0.54    0.45     0.87     0.10  0.45  0.01  
##  1     4       79253.01 79452.07 0.51    0.53     0.82     0.13  0.45  0.01  
##  1     5       79198.41 79439.38 0.54    0.49     0.82     0.05  0.43  0.01  
##  1     6       79157.81 79440.69 0.52    0.56     0.70     0.05  0.26  0.01  
##  1     7       79127.69 79452.48 0.52    0.62     0.67     0.04  0.23  0.01  
##  1     8       79093.92 79460.61 0.56    0.58     0.72     0.04  0.23  0.01  
##  1     9       79085.02 79493.62 0.58    0.50     0.73     0.02  0.21  0.02  
##  2     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  2     2       79221.45 79373.37 0.60    0.87     0.88     0.49  0.51  0.01  
##  2     3       79119.17 79349.67 0.55    0.68     0.83     0.28  0.41  0.01  
##  2     4       79007.67 79316.75 0.57    0.60     0.82     0.13  0.38  0.01  
##  2     5       78978.84 79366.48 0.56    0.60     0.82     0.10  0.30  0.01  
##  2     6       78934.24 79400.47 0.60    0.59     0.83     0.09  0.32  0.01  
##  2     7       78967.67 79512.47 0.56    0.58     0.81     0.07  0.22  0.97  
##  2     8       78963.30 79586.68 0.57    0.55     0.82     0.05  0.24  0.13  
##  2     9       78949.02 79650.98 0.59    0.55     0.79     0.04  0.23  0.04  
##  3     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  3     2       79171.36 79396.62 0.31    0.76     0.77     0.49  0.51  0.08  
##  3     3       79173.56 79440.72 0.37    0.45     0.79     0.10  0.53  0.12  
##  3     4       79086.06 79395.13 0.49    0.46     0.85     0.13  0.58  0.01  
##  3     5       79081.65 79432.62 0.46    0.49     0.79     0.09  0.48  0.06  
##  3     6       79093.82 79486.70 0.40    0.50     0.69     0.09  0.24  0.58  
##  3     7       79039.87 79474.67 0.49    0.37     0.72     0.05  0.34  0.01  
##  3     8       79023.57 79500.27 0.51    0.44     0.73     0.05  0.33  0.02  
##  3     9       79007.36 79525.97 0.55    0.50     0.75     0.02  0.33  0.01  
##  6     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  6     2       78984.37 79356.30 0.42    0.80     0.84     0.49  0.51  0.01  
##  6     3       78965.36 79525.87 0.50    0.67     0.80     0.19  0.43  0.01  
##  6     4       78937.22 79686.33 0.50    0.63     0.77     0.18  0.31  0.01  
##  6     5       78951.32 79889.01 0.52    0.64     0.74     0.13  0.29  0.38  
##  6     6       78922.42 80048.70 0.61    0.62     0.79     0.11  0.26  0.04  
##  6     7       78931.88 80246.75 0.62    0.65     0.83     0.09  0.23  0.43  
##  6     8       78941.80 80445.25 0.64    0.63     0.82     0.08  0.19  0.50  
##  6     9       78909.55 80601.58 0.66    0.62     0.83     0.06  0.20  0.12
\end{verbatim}

\begin{verbatim}
## tidyLPA analysis using mplus: 
## 
##  Model Classes AIC      BIC      Entropy prob_min prob_max n_min n_max BLRT_p
##  1     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  1     2       79305.15 79420.39 0.60    0.85     0.90     0.41  0.59  0.00  
##  1     3       79255.92 79413.08 0.53    0.68     0.81     0.15  0.54  0.00  
##  1     4       79185.44 79384.50 0.59    0.62     0.79     0.05  0.50  0.00  
##  1     5       79122.99 79363.96 0.64    0.60     0.81     0.05  0.51  0.00  
##  1     6       79102.55 79385.43 0.66    0.60     0.82     0.03  0.51  0.00  
##  1     7       79096.03 79420.81 0.62    0.53     0.78     0.01  0.39  0.13  
##  1     8       79068.33 79435.02 0.69    0.58     0.83     0.01  0.51  0.02  
##  1     9       79065.91 79474.51 0.63    0.41     0.80     0.01  0.45  0.00  
##  2     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  2     2       79220.63 79372.54 0.60    0.87     0.89     0.50  0.50  0.00  
##  2     3       79100.80 79331.30 0.58    0.77     0.81     0.18  0.45  0.00  
##  2     4       79000.42 79309.49 0.59    0.66     0.79     0.14  0.38  0.00  
##  2     5       78946.87 79334.52 0.62    0.59     0.81     0.08  0.36  0.00  
##  2     6       78926.11 79392.34 0.59    0.60     0.80     0.08  0.24  0.08  
##  2     7       78902.41 79447.21 0.58    0.62     0.81     0.08  0.25  0.03  
##  2     8       78900.48 79523.86 0.57    0.57     0.82     0.08  0.21  0.24  
##  2     9       78884.99 79586.95 0.62    0.56     0.79     0.01  0.24  1.00  
##  3     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  3     2       79090.94 79316.20 0.77    0.62     0.98     0.09  0.91  0.00  
##  3     3       79084.97 79352.14 0.57    0.66     0.89     0.09  0.64  1.00  
##  3     4       79047.05 79356.12 0.79    0.58     0.97     0.05  0.85  0.00  
##  3     5       79023.67 79374.65 0.79    0.56     0.95     0.01  0.80  0.03  
##  3     6       79017.46 79410.34 0.79    0.45     0.96     0.01  0.83  0.67  
##  3     7       78998.02 79432.82 0.63    0.56     0.79     0.01  0.41  0.67  
##  3     8       78992.36 79469.07 0.62    0.54     0.82     0.02  0.48  0.33  
##  3     9       78976.63 79495.24 0.65    0.52     0.81     0.03  0.44  0.67  
##  4     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  4     2       78988.37 79250.30 0.38    0.77     0.82     0.48  0.52  0.00  
##  4     3       78942.17 79282.68 0.47    0.59     0.83     0.13  0.51  0.09  
##  4     4       78916.22 79335.30 0.51    0.56     0.78     0.11  0.41  0.29  
##  4     5       78887.30 79384.96 0.64    0.60     0.99     0.01  0.39  0.27  
##  4     6       78876.11 79452.35 0.58    0.60     0.78     0.03  0.32  0.31  
##  4     7       78865.12 79519.93 0.55    0.47     0.76     0.07  0.29  0.67  
##  4     8       78862.98 79596.37 0.64    0.50     0.85     0.04  0.47  1.00  
##  4     9       78859.93 79671.90 0.65    0.58     0.94     0.01  0.44  0.67  
##  5     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  5     2       79090.89 79426.16 0.81    0.71     0.98     0.11  0.89  0.00  
##  5     3       79057.51 79544.69 0.70    0.62     0.94     0.06  0.78  0.43  
##  5     4       79024.23 79663.33 0.79    0.59     0.97     0.01  0.81  0.16  
##  5     5       79001.55 79792.57 0.79    0.65     1.00     0.01  0.75  0.02  
##  5     6       78960.55 79903.48 0.87    0.53     1.00     0.01  0.84  0.00  
##  5     7       79005.61 80100.45 0.81    0.52     1.00     0.01  0.75  0.00  
##  5     8       78958.75 80205.52 0.91    0.65     1.00     0.01  0.82  0.00  
##  5     9       78911.08 80309.75 0.72    0.50     0.98     0.01  0.51  0.11  
##  6     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  6     2       78980.55 79352.48 0.41    0.75     0.86     0.42  0.58  0.00  
##  6     3       78946.26 79506.78 0.55    0.72     0.85     0.17  0.50  0.25  
##  6     4       78921.55 79670.65 0.61    0.74     0.81     0.12  0.40  0.67  
##  6     5       78905.25 79842.94 0.64    0.65     1.00     0.01  0.38  0.00  
##  6     6       78889.78 80016.05 0.66    0.68     0.96     0.02  0.33  0.33  
##  6     7       78880.06 80194.92 0.67    0.67     1.00     0.01  0.29  0.00  
##  6     8       78844.83 80348.28 0.70    0.66     0.99     0.01  0.38  0.50  
##  6     9       78871.79 80563.83 0.74    0.72     1.00     0.01  0.39  0.60
\end{verbatim}

\begin{verbatim}
## tidyLPA analysis using mplus: 
## 
##  Model Classes AIC      BIC      Entropy prob_min prob_max n_min n_max BLRT_p
##  1     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  1     2       79305.15 79420.39 0.60    0.85     0.90     0.41  0.59  0.00  
##  1     3       79236.08 79393.23 0.68    0.58     0.90     0.05  0.55  0.00  
##  1     4       79185.44 79384.50 0.59    0.62     0.79     0.05  0.50  0.00  
##  1     5       79122.99 79363.96 0.64    0.60     0.81     0.05  0.51  0.00  
##  1     6       79102.55 79385.43 0.66    0.60     0.83     0.03  0.51  0.00  
##  1     7       79082.23 79407.02 0.69    0.60     0.83     0.01  0.51  0.00  
##  1     8       79068.00 79434.69 0.65    0.51     0.78     0.01  0.43  0.00  
##  1     9       79045.95 79454.55 0.65    0.56     0.79     0.02  0.42  0.00  
##  2     1       79926.21 79999.54 1.00    1.00     1.00     1.00  1.00        
##  2     2       79220.63 79372.54 0.60    0.87     0.89     0.50  0.50  0.00  
##  2     3       79100.80 79331.30 0.58    0.77     0.81     0.18  0.45  0.00  
##  2     4       79000.42 79309.49 0.59    0.66     0.79     0.14  0.38  0.00  
##  2     5       78946.87 79334.52 0.62    0.59     0.81     0.08  0.36  0.00  
##  2     6       78926.11 79392.34 0.59    0.60     0.80     0.08  0.24  0.07  
##  2     7       78902.41 79447.21 0.58    0.62     0.81     0.08  0.25  0.00  
##  2     8       78894.18 79517.57 0.62    0.55     0.80     0.03  0.34  0.67  
##  2     9       78883.07 79585.03 0.62    0.60     0.83     0.04  0.16  1.00  
##  3     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  3     2       79090.94 79316.20 0.77    0.62     0.98     0.09  0.91  0.00  
##  3     3       79070.64 79337.81 0.85    0.63     0.98     0.01  0.90  0.00  
##  3     4       79045.48 79354.55 0.81    0.61     0.97     0.03  0.85  0.00  
##  3     5       79013.99 79364.97 0.79    0.62     0.96     0.01  0.80  0.00  
##  3     6       79006.55 79399.44 0.76    0.50     0.94     0.02  0.76  0.24  
##  3     7       78996.75 79431.55 0.68    0.61     0.83     0.01  0.43  0.18  
##  3     8       78973.50 79450.20 0.79    0.45     0.95     0.01  0.78  0.00  
##  3     9       78976.27 79494.88 0.62    0.54     0.84     0.01  0.41  1.00  
##  4     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  4     2       78988.37 79250.30 0.38    0.77     0.82     0.48  0.52  0.00  
##  4     3       78942.17 79282.68 0.47    0.59     0.83     0.13  0.51  0.05  
##  4     4       78916.22 79335.30 0.51    0.56     0.78     0.11  0.41  0.38  
##  4     5       78882.99 79380.65 0.55    0.58     0.99     0.01  0.36  0.27  
##  4     6       78876.11 79452.35 0.58    0.60     0.78     0.03  0.32  0.38  
##  4     7       78860.74 79515.56 0.60    0.60     0.97     0.02  0.29  0.43  
##  4     8       78828.13 79561.52 0.66    0.54     0.97     0.01  0.35  0.33  
##  4     9       78826.80 79638.77 0.65    0.53     0.97     0.01  0.38  0.00  
##  5     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  5     2       79090.89 79426.16 0.81    0.71     0.98     0.11  0.89  0.00  
##  5     3       79053.92 79541.10 0.68    0.68     0.92     0.13  0.72  0.25  
##  5     4       79012.99 79652.08 0.93    0.71     0.99     0.01  0.90  0.04  
##  5     5       78980.40 79771.42 0.78    0.67     1.00     0.01  0.72  0.10  
##  5     6       78960.55 79903.48 0.87    0.53     1.00     0.01  0.84  0.00  
##  5     7       78937.28 80032.13 0.88    0.63     1.00     0.01  0.79  0.24  
##  5     8       78945.36 80192.12 0.75    0.66     1.00     0.01  0.53  0.24  
##  5     9       78890.04 80288.71 0.77    0.50     1.00     0.01  0.56  0.00  
##  6     1       79157.63 79340.98 1.00    1.00     1.00     1.00  1.00        
##  6     2       78980.55 79352.48 0.41    0.75     0.86     0.42  0.58  0.00  
##  6     3       78943.69 79504.21 0.51    0.64     0.88     0.20  0.58  0.67  
##  6     4       78910.45 79659.56 0.64    0.73     0.92     0.03  0.49  0.10  
##  6     5       78890.91 79828.60 0.61    0.56     0.85     0.08  0.47  0.36  
##  6     6       78837.12 79963.39 0.73    0.74     0.96     0.01  0.47  0.00  
##  6     7       78854.88 80169.74 0.68    0.58     0.94     0.02  0.42  0.67  
##  6     8       78843.89 80347.34 0.81    0.72     1.00     0.01  0.58  0.00  
##  6     9       78871.79 80563.83 0.74    0.72     1.00     0.01  0.39  0.60
\end{verbatim}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

This section highlights three general recommendations. First, scholars taking a
person-oriented approach should emphasize reproducibility in carrying out
analyses. This is in part due to the exploratory and interpretative nature of
person-oriented approaches. To this end, presenting multiple models, as in
Pastor et al.~(2007), should be encouraged, rather than presenting one solution.
In addition, having multiple analysts review the solutions found is encouraged.
As part of this recommendation, we suggest that researchers consider how their
analyses can be reproduced by other analysts outside of the research team:
Sharing code and data is an important part of this work. Also related,
researchers should consider how profiles are replicated across samples.

@@

First, we note that developing a tool that emphasized both rigor and access has
been, so far, well-received. This suggests that there is an audience (or a
market) for tools to carry out sophisticated tools that may be otherwise
out-of-reach. Tools do not need to be hard to use, a point made by developers
of, for example, tools to carry out highly-sophisticated Bayesian methods using
the most cutting-edge tools (Bürkner \& others, 2017, p. @makowski2019). We think
that tidyLPA speaks to this, too.

@@

\leavevmode\hypertarget{ref-R-tidyLPA}{}%
Rosenberg, J. M., Beymer, P. N., Anderson, D. J., Lissa, C. van, \& Schmidt, J. A. (2018). TidyLPA: An r package to easily carry out latent profile analysis (lpa) using open-source or commercial software. \emph{Journal of Open Source Software}, \emph{3}(30), 978. \url{https://doi.org/10.21105/joss.00978}
